experiment 1

### 2021-10-06 experiments/experiment 1/experiment-1.Rmd
Fix something more

library(microxanoxBeta)
if (packageVersion("microxanoxBeta") < package_version("0.2.3")) {
  stop("microxanox version needs to be at least 0.2.3!")
}
library(tidyverse)
library(patchwork)
library(here)
source(here("experiments/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 8)
eval_dynamics_flag <- FALSE
```

@@

num_div_treatment_levels <- 20
```

@@

```{r}
display_diversity(
  400,
  var_expt = var_expt,
  num_CB_strains = num_CB_strains,
  num_SB_strains = num_SB_strains,
  num_PB_strains = num_PB_strains
)
```

@@

```{r}
options(mc.cores = 6)
```

@@

grid_num_a <- 1000 #usually 1000 ## number of a_0 values
a_Os <- 10^seq(-7, -0.5, length=grid_num_a) ## sequence of a_0 values
grid_num_N <- 2 ## number of N values
initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)

parameter <- new_ss_by_a_N_parameter(
  dynamic_model = parameter$dynamic_model,
  event_definition = parameter$event_definition,
  event_interval = 1000000,
  noise_sigma = parameter$noise_sigma,
  minimum_abundances = minimum_abundances,
  sim_duration = 1000000,
  sim_sample_interval = 1000000,
  log10a_series = parameter$log10a_series,
  solver_method = parameter$solver_method,
  ss_expt = ss_expt
)
rm(minimum_abundances, grid_num_a, a_Os, grid_num_N, initial_CBs, initial_PBs, initial_SBs, ss_expt)
```

@@

```{r run_experiment, eval = eval_dynamics_flag}

@@

Bring in various stable state datasets
```{r eval = FALSE}
## sim length 80'000, 20 x 20 factorial, reference maximum diversity

>>>>

library(microxanoxBeta)
if (packageVersion("microxanoxBeta") < package_version("0.2.3")) {
  stop("microxanox version needs to be at least 0.2.3!")
}
library(tidyverse)
library(patchwork)
library(here)
source(here("experiments/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 8)
eval_dynamics_flag <- TRUE
```

@@

## num_div_treatment_levels <- 20

num_div_treatment_levels <- 3 ## FOR TEST

@@

```{r eval = FALSE}
display_diversity(
  400, ##seems to be necessary to be smaller than num_div_treatment_levels
  var_expt = var_expt,
  num_CB_strains = num_CB_strains,
  num_SB_strains = num_SB_strains,
  num_PB_strains = num_PB_strains
)
```

@@

```{r}
options(mc.cores = 7)
```

@@

## grid_num_a <- 1000 #usually 1000 ## number of a_0 values
grid_num_a <- 100 ## FOR TEST

a_Os <- 10^seq(-7, -0.5, length=grid_num_a) ## sequence of a_0 values
grid_num_N <- 2 ## number of N values
initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)

parameter <- new_ss_by_a_N_parameter(
  dynamic_model = parameter$dynamic_model,
  event_definition = parameter$event_definition,
  event_interval = 1000000,
  noise_sigma = parameter$noise_sigma,
  minimum_abundances = minimum_abundances,
  sim_duration = 1000000,
  sim_sample_interval = 1000000,
  log10a_series = parameter$log10a_series,
  solver_method = parameter$solver_method,
  ss_expt = ss_expt
)
rm(minimum_abundances, grid_num_a, a_Os, grid_num_N, initial_CBs, initial_PBs, initial_SBs, ss_expt)
saveRDS(parameter, here("experiments/experiment 1/data/TEST_parameter.RDS"))
saveRDS(var_expt, here("experiments/experiment 1/data/TEST_var_expt.RDS"))
```

@@

```{r run_experiment, eval = eval_dynamics_flag}
parameter <- readRDS(here("experiments/experiment 1/data/TEST_parameter.RDS"))
var_expt <- readRDS(here("experiments/experiment 1/data/TEST_var_expt.RDS"))

@@

Bring in various stable state datasets
```{r eval = TRUE}
## sim length 80'000, 20 x 20 factorial, reference maximum diversity
